%\documentclass[11pt,a4paper]{mycv}
\documentclass[11pt,letterpaper]{mycv}

\mycvtheme[blue,roman]{mine}
\usepackage{amsmath}

% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}		% if you want to change the width of the column with the dates
\AtBeginDocument{\setlength{\maketitlenamewidth}{8cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Marc T.}
\familyname{\mbox{Henry de Frahan}}
%\title{Applied Mathematics engineer}              
%\address{Rue E. Semal 4}{1310 La Hulpe, Belgium}
\address{409 E. Kingsley St Apt 2.}{Ann Arbor, MI, 48104}
\mobile{(734)747-0156}                   
\email{marchdf@umich.edu}                  
%\phone{phone (optional)}                  
%\fax{fax (optional)}                      
%\extrainfo{additional information (optional)}
%\quote{Some quote (optional)}                

\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle%\ignorespaces
\vspace*{-0.5cm}%

\section{Education}%
\cventry{2011-present}{Ph.D. in Mechanical Engineering}{University of Michigan}{Ann Arbor, MI}{}{\textit{Research focus:} Numerical simulations of compressible multiphase flows\newline\textit{Advisor:} Prof. E. Johnsen}%
\cventry{2009-2011}{M.S. in Applied Mathematics Engineering}{Université Catholique de Louvain}{Belgium}{completed with \textit{High Distinction}}{\textit{Specialization:} Numerical simulation and modeling \\\textit{Thesis:} Implementation of a Discontinuous Galerkin Method for hyperbolic PDEs on GPUs\newline \textit{ Thesis supervisors:} Dr. J-F Remacle, Dr. P. Chatelain, Dr. V. Legat.}%
\cventry{2007-2009}{B.S. in Applied Mathematics Engineering}{Université Catholique de Louvain}{Belgium}{graduated with \textit{Distinction}. \textit{Minor:} Physics}{}%

\section{Research Interests}%
\cventry{}{Fluid mechanics - multiphase flows, hydrodynamic instabilities, turbulence}{}{}{}{}%
\cventry{}{Plasma physics - solar wind turbulence, supernovae explosions}{}{}{}{}%
\cventry{}{High order numerical methods for computational fluid dynamics}{}{}{}{}%
\cventry{}{High performance computing with graphics processing units}{}{}{}{}{}%

\section{Relevant Experience}%
\cventry{2014-present}{President}{Mechanical Engineering Graduate Council}{University of Michigan}{}{Promote social, academic and professional development for engineering graduate students}%
\cventry{2014-present}{Representative for Department of Mechanical Engineering}{Graduate Student Advisory Committee}{University of Michigan}{}{Identify and plan activities to promote community among engineering graduate students}%
\cventry{Summer 2014}{Participant}{International High Performance Computing Summer School 2014}{Budapest, Hungary}{}{Invited to attend NSF workshop to learn new paradigms in scientific computing}%
\cventry{Fall 2013}{Graduate Student Instructor}{ME/AERO 523: Computational Fluid Dynamics}{Prof. E. Johnsen}{}{}%
\cventry{Summer 2012}{Student Intern}{Lawrence Livermore National Lab.}{Livermore}{CA}{Comparing Beryllium strength models with experimental data\newline\textit{Supervisors}: Dr. B. Remington and Dr. R. Cavallo}%
\cventry{Spring 2012}{Long-term Participant}{Computational Methods in High Energy Density Plasmas}{}{}{Invited to attend a workshop by the Institute for Pure and Applied Mathematics at UCLA}%
\cventry{Summer 2010}{Student Intern}{Lawrence Livermore National Lab.}{Livermore}{CA}{Studied hydrodynamic instabilities in inertial confinement fusion targets\newline Characterized growth factors during capsule compression\newline \textit{Supervisors}: Dr. L. J. Suter and Dr. D. S. Clark}%
\cventry{Summer 2009}{Student Intern}{Lawrence Livermore National Lab.}{Livermore}{CA}{Studied hot electron signatures and capsule preheat in the context of inertial confinement fusion as developed at the National Ignition Facility\newline \textit{Supervisors}: Dr. L. J. Suter and Dr. C. A. Thomas}% 
\cventry{Summer 2008}{Student Intern}{Lawrence Livermore National Lab.}{Livermore}{CA}{Studied and optimized National Ignition Facility inertial confinement fusion target geometries using view factor calculations\newline \textit{Supervisors}: Dr. L. J. Suter and Dr. C. A. Thomas}%
%\cventry{Summer 2007}{Intern}{Meridian Construction Inc.}{Spokane WA}{USA}{Worked on a construction site and maintained office databases.}
%\cventry{2006-2007}{Front Desk Assistant}{Georgetown University Library}{Washington D.C}{USA}{}%{Responsible for media check-out and supervision of the computer laboratory.}
%\cventry{2007-present}{Tutor \textnormal{in high-school and college Mathematics, Science, Latin and Ancient Greek}}{}{}{}{}

\section{Fellowships and Awards}%
\cvaward{Rackham Predoctoral Fellowship}{2015}{University of Michigan}{}%
\cvaward{Rackham Centennial Fellowship}{2013}{University of Michigan}{}%
\cvaward{Poster Winner}{\,LLNL 2012 Summer Poster Session}{Livermore, CA}{}%

\section{Peer-reviewed Publications}%
\cvarticle{M. T. Henry de Frahan, J. L. Belof, R. M. Cavallo, V. A. Raevsky, O. N. Ignatova, A. Lebedev, D. S. Ancheta, B. S. El-dasher, J. N. Florando, G. F. Gallegos, E. Johnsen and M. M. LeBlanc}{Experimental and Numerical Investigations of Beryllium Strength Models Using the Rayleigh-Taylor Instability}{featured article in J. Appl. Phys.}{\,117(22):225901}{2015}{\textbf{}}%
\cvarticle{M. T. Henry de Frahan, S. Varadan, and E. Johnsen}{A new limiting procedure for discontinuous Galerkin methods applied to compressible multiphase flows with shocks and interfaces}{J. Comput. Phys.}{280(0):489 -- 509}{2015}{}%
\cvarticle{M. T. Henry de Frahan, P. Movahed, and E. Johnsen}{Numerical simulations of a shock interacting with successive interfaces using the Discontinuous Galerkin method: the multilayered Richtmyer-Meshkov and Rayleigh-Taylor instabilities}{Shock Waves}{25(4):329--345}{2015}{}%
\cvarticle{C. A. Di Stefano, G. Malamud, M. T. Henry de Frahan, C. C. Kuranz, A. Shimony, S. R. Klein, R. P. Drake, E. Johnsen, D. Shvarts, V. A. Smalyuk, and D. Martinez}{Observation and modeling of mixing-layer development in high-energy-density, blast-wave-driven shear flow}{Phys. Plasmas}{21(5):056306}{2014}{}%
\cvarticle{M. T. Henry de Frahan and E. Johnsen}{Mixing in blast-driven hydrodynamic instabilities}{In preparation for J. Fluid Mech.}{2015}{}{}%



\section{Conference Proceedings}%
\cvarticle{M. T. Henry de Frahan and E. Johnsen}{High-order Discontinuous Galerkin Methods Applied to Multiphase Flows}{23d AIAA Computational Fluid Dynamics Conference. American Institute of Aeronautics and Astronautics}{submitted}{2015}{}%
\cvarticle{M. T. Henry de Frahan and E. Johnsen}{Discontinuous Galerkin method for multifluid Euler equations}{In 21st AIAA Computational Fluid Dynamics Conference. American Institute of Aeronautics and Astronautics}{doi: 10.2514/6.2013-2595}{2013}{}%
\cvarticle{M. T. Henry de Frahan, P. Movahed, and E. Johnsen}{Investigating the multilayered Richtmyer-Meshkov instability with high-order accurate numerical methods}{In 29th International Symposium on Shock Waves}{}{2013}{}%

\section{Presentations}%
\cvpres{M. T. Henry de Frahan, E. Johnsen}{Numerical simulations of hydrodynamic instabilities with GPUs}{IPAM Computational Methods in High Energy Density Plasmas Reunion Conference}{Dec. 2014}{Lake Arrowhead, CA}{}%
\cvpres{M. T. Henry de Frahan, E. Johnsen}{Hydrodynamic instabilities in blast-driven systems}{APS $67^\text{th}$ Meeting of the Division of Fluid Dynamics}{Nov. 2014}{San Francisco, CA}{}%
\cvpres{M. T. Henry de Frahan, R. P. Drake, E. Johnsen}{Hydrodynamic instabilities of finite width layers}{APS $56^\text{th}$ Meeting of the Division of Plasma Physics}{Oct. 2014}{New Orleans, LA}{}%
\cvpres{E. Johnsen, M. T. Henry de Frahan, S. A. Beig}{Numerical simulations of gas-liquid interfaces in compressible flows}{AIAA Aviation Forum}{Jun. 2014}{Atlanta, GA}{}%
\cvpres{M. T. Henry de Frahan, E. Johnsen}{Blast-driven hydrodynamic instability}{APS $66^{\text{th}}$ Meeting of the Division of Fluid Dynamics}{Nov. 2013}{Pittsburgh, PA}{}%
\cvpres{M. T. Henry de Frahan, J. L. Belof, R. M. Cavallo, O. Ignatova, E. Johnsen, B. A. Remington, V. Raevsky}{Analysis of recent Beryllium Rayleigh-Taylor experiments}{Fundamentals of Pu Workshop XIII}{Sep. 2013}{Sarov, Russia}{}%
\cvpres{M. T. Henry de Frahan, P. Movahed, E. Johnsen}{Investigating the multi-layered Richtmyer-Meshkov instability with high-order accurate numerical methods}{$29^{\text{th}}$ International Symposium on Shock Waves}{Jul. 2013}{Madison, WI}{}%
\cvpres{M. T. Henry de Frahan, E. Johnsen}{Discontinuous Galerkin method for multifluid Euler equations}{$21^{\text{st}}$ AIAA Computational Fluid Dynamics Conference}{Jun. 2013}{San Diego, CA}{}%
\cvpres{M. T. Henry de Frahan, J. L. Belof, R. M. Cavallo, O. Ignatova, E. Johnsen, B. A. Remington, V. Raevsky}{\link[\textbf{Beryllium strength under extreme dynamic loading conditions}]{http://meeting.aps.org/Meeting/DPP12/Event/176052}}{APS $54^{\text{th}}$ Meeting of the Division of Plasma Physics}{Oct. 2012}{Providence, RI}{}%
%\cvpres{M. T. Henry de Frahan, J. L. Belof, R. M. Cavallo, O. Ignatova, E. Johnsen, B. A. Remington, V. Raevsky}{Beryllium strength under extreme dynamic loading conditions}{Annual MIPSE Poster Symposium}{October 2012}{Michigan State University, MI}{}
\cvpres{M. T. Henry de Frahan, D. S. Clark, L. J. Suter}{Hydrodynamic instabilities in inertial confinement fusion targets}{WCI Summer Presentation}{Sept. 2010}{Livermore, CA}{}%
\cvpres{M. T. Henry de Frahan, C. A. Thomas, L. J. Suter}{Hot electron signatures and preheat}{WCI Summer Presentation}{Sept. 2009}{Livermore, CA}{}%
\cvpres{M. T. Henry de Frahan, C. A. Thomas, L. J. Suter}{Achieving symmetry without the inner cone}{WCI Summer Presentation}{Sept. 2008}{Livermore, CA}{}%
%\cvpres{M. T. Henry de Frahan, C. A. Thomas, L. J. Suter}{Achieving symmetry without the inner cone}{ LLNL Summer Poster Session}{August 2008}{Livermore, CA}{}

\section{Memberships}%
\cventry{2012-present}{American Physical Society}{}{student member}{}{}%
\cventry{2012-present}{American Institute of Aeronautics and Astronautics}{}{student member}{}{}%
\cventry{2011-2013}{\link[Center for Radiative Shock Hydrodynamics]{http://aoss-research.engin.umich.edu/crash/}}{U. of Michigan}{student member}{}{}%

\section{Computer Skills}%
\cvcomputer{Scientific programing}{C/C++, Python, Bash, Git, \textsc{C} for \textsc{CUDA}, \textsc{MPI}, OpenMP, \LaTeX, VisIt, Gmsh, Matlab, Hydra, Ares, Yorick, \textsc{ITS} Monte-Carlo Codes}%
\cvcomputer{Operating systems}{GNU/Linux, Windows}%

\section{Languages}%
\cvlanguage{English}{fluent}{First mother tongue}%
\cvlanguage{French}{fluent}{Second mother tongue}%
\cvlanguage{Dutch}{proficient}{6 years in secondary school}%
\end{document}
